---
title: "Patient Post Match Report"
output:
  html_document: default
---

```{r setup, include=FALSE}
library(healthcareai)
library(dplyr)
library(knitr)
library(tidyr)
knitr::opts_chunk$set(echo = TRUE)

connectionString <- '
  driver={SQL Server};
  server=agca-edwdev;
  database=SAM;
  trustedConnection=true'

```
##verification
```{r verification, include=FALSE}
 query <- "
SELECT source1 as Source, source2,count(*)as  MatchCNT
  FROM [SAM].[MasterDataMonitoring].[PostMatchDetail]
  group by source1, source2"

matchmatrix<- selectData(connectionString,query)
```


##Match Combinations

```{r interactions , echo=FALSE}
 query <- "
SELECT source1 as Source, source2,count(*)as  MatchCNT
  FROM [SAM].[MasterDataMonitoring].[PostMatchDetail]
  group by source1, source2"

matchmatrix<- selectData(connectionString,query)
matchmatrix <- spread(matchmatrix,source2, MatchCNT)
kable(matchmatrix)



query <- "
  --total matches
  SELECT count(*)
  FROM [SAM].[MasterDataMonitoring].[PostMatchDetail]"

```





```{r scoredist , include=FALSE}

query <- '/****** Script for SelectTopNRows command from SSMS  ******/
SELECT 
      [Score]
      ,[ScoreCNT]
  FROM [SAM].[MasterDataMonitoring].[PostMatchScoreFrequency]'
ScoreFreq <- selectData(connectionString,query)


"SELECT min([TotalScore]), max(totalscore)
  
  FROM [MultiVueDataSync].[Patient].[ScoringDetails]"
```



## Score Distribution



After the MultiVue match process is run a data sync was run to retrieve data from MultiVue.  This data is a score for each pair of records that broke the matching threshold. The distribution of score shows which scores contain the most matches.


```{r Distribution, echo=FALSE }
plot(ScoreFreq, type = 'h', lwd = 10, main = 'Score Distribution', lend = 'square'  )

```

 

```{r top scores, echo=FALSE}
tot <- sum(ScoreFreq$ScoreCNT)
top8 <- ScoreFreq %>%
  arrange(desc(ScoreCNT)) %>%
  head(n=8) %>%
  arrange(desc(ScoreCNT))
```
From this distribution the prominent peaks are if the most interest in finding the merge threshold. Preform a validation test on these peaks to find which neighborhood the merge threshold should be in.The peaks account for `r sprintf("%3.1f",100*sum(top8$ScoreCNT)/tot)`% of the possible matches.


```{r top scores table, echo=FALSE}
kable(top8)

```

Those scoring groups have the following score breakdowns:

```{r scoredetails , echo= FALSE}
query <- "SELECT  distinct
      m.[Score]
      --,[ScoreDetailsID]
      --,[MatchRuleName]
     -- ,[Hash]
     -- ,[ScoreDetailGroupID]
      ,[GroupName]
      ,[GroupScore]
     -- ,[ThresholdApplied]
      --,[ScoreBeforeLimitApplied]
      --,[ScoreDetailGroupFieldID]
      ,[FieldIdentifier]
      ,[MatchType]
      ,[FieldScore]
    --  ,[ScoreReduction]
  FROM [SAM].[MasterDataMonitoring].[PostMatchScoreDetail] m
  where m.Score in (SELECT top 5
      [Score]
  FROM [SAM].[MasterDataMonitoring].[PostMatchScoreFrequency] 
  order by ScoreCNT desc)"
scoredetails <- selectData(connectionString,query)
kable(scoredetails)
```



##Validation of Score Groups
Each score group will be evaliatied using the rule of 3.  To determine if it is a positive (all pairs identify the same person) or a negative (all pairs do not identify the same person) set.  The merge threshold must be set at or above a positive set.

``` {r validation , echo= FALSE}

query <- "SELECT  
      [MatchID]
      ,[VirtualEntity1Id]
      ,[VirtualEntity2Id]
      ,[Domain]
      ,[Score]
      ,[Source1]
      ,[Source2]
      ,[EntityID1]
      ,[EntityID2]
      ,[ID1]
      ,[ID2]
      ,[Identifier1]
      ,[Identifier2]
      ,[PatientFirstNM1]
      ,[PatientFirstNM2]
      ,[PatientLastNM1]
      ,[PatientLastNM2]
      ,[SSN1]
      ,[SSN2]
  FROM [SAM].[MasterDataMonitoring].[PostMatchValidationSample]"
validationset  <- selectData(connectionString,query)
kable(validationset)


```