---
title: "Shared Person Patient Profiling"
output: html_document
---


```{r setup, include=FALSE}
library(healthcareai)
library(dplyr)
library(knitr)
knitr::opts_chunk$set(echo = TRUE)
DisplayPHI <- TRUE

# Set connection string for client
connectionString <- "
  driver={SQL Server};
  server=AGCA-edwdev;
  database=SAM;
  trustedConnection=true"


query <- "SELECT DatabaseNM + '.' + SchemaNM + '.' + ViewNM
FROM EDWAdmin.CatalystAdmin.TableBASE
WHERE tableID IN
(
    SELECT [SourceEntityID]
    FROM [EDWAdmin].[CatalystAdmin].[BindingDependencyBASE]
    WHERE bindingID =
    (
        SELECT [BindingID]
        FROM EDWAdmin.CatalystAdmin.BindingBASE
        WHERE DestinationEntityID =
        (
            SELECT tableID
            FROM EDWAdmin.CatalystAdmin.TableBASE
            WHERE schemaNM = 'Person'
                  AND ViewNM = 'SourcePatient'
        )
    )
);"

DependencyList <- selectData(connectionString,query)

```

##Table Dependencies
The dependencies for SourcePatient are **`r as.character(DependencyList[,1])`**

## Fill Rates
```{r fillrates, echo= FALSE}
query <- "
SELECT TOP 10
      [AttributeNM]
      ,[RowSourceDSC]
      ,[RowCNT]
      ,[ValueCNT]
      ,[DistinctValueCNT]
      ,[NullCNT]
      ,BlankCNT
      ,100-100*(NullCNT + BlankCNT)/cast(RowCNT as float) AS FillPCT
  FROM [SAM].[SourcePatientProfiling].[SummaryPatientDescriptiveStatisticsBySource]
  order by 100-100*(NullCNT + BlankCNT)/cast(RowCNT as float) "
FillRate <- selectData(connectionString,query)

 query <- "select count(*)
from shared.Person.SourcePatient"
count <-  selectData(connectionString,query)
 count <- count[1,1]

query <-"SELECT   
      [RowSourceDSC]
      ,100-100*(sum([NullCNT]) +sum(BlankCNT))/cast(sum([RowCNT]) as float) as FillPCT
  FROM [SAM].[SourcePatientProfiling].[SummaryPatientDescriptiveStatisticsBySource]
group by rowsourceDSC"
FillRateBySource <- selectData(connectionString,query)

query <- " select  columnNM as AttributeNM
  from EDWAdmin.CatalystAdmin.TableBASe T
  inner join   EDWAdmin.CatalystAdmin.ColumnBASE C
  on T.tableID = C.tableID
  where databaseNM = 'shared'
  and schemanm = 'Person'
  and tableNM = 'SourcePatientBASE'
  and ColumnNM not in ('BindingID','BindingNM', 'LastLoadDTS','ProviderID','RowSourceDSC')

  Except

  SELECT distinct
      [AttributeNM]

  
  FROM [SAM].[SourcePatientProfiling].[SummaryPatientDescriptiveStatisticsBySource]"

UnUsedList <- selectData(connectionString,query,)
```
For a field to be useful it must contain data. The fields **`r as.character(UnUsedList[,1])`** contain only NULLS and are not represented in this analysis. The lowest 10 fill rates in Shared.Person.SourcePatient are in the table below. Additional information can be found in the EDW at SAM.SourcePatientProfiling.SummaryPatientDescriptiveStatisticsBySource

```{r tableFillRate, echo= FALSE}
FillRate <- FillRate %>% 
 mutate(RowCNT = count, NullCNT = count - ValueCNT) %>%
 mutate( FillPCT = 100-100*(NullCNT + BlankCNT)/RowCNT) %>%
select(AttributeNM, RowSourceDSC, RowCNT, ValueCNT, DistinctValueCNT, NullCNT,BlankCNT, FillPCT)
kable(FillRate, digits =1)
```

## Supicious Data Type 

```{r datatype, include=FALSE}
query <-"SELECT  [AttributeNM],
                [RowSourceDSC],
                [RowCNT],
                [NumericValueCNT],
                [DateValueCNT],
                [TextValueCNT]



FROM [SAM].[SourcePatientProfiling].[SummaryPatientDescriptiveStatisticsBySource] summ

WHERE(numericValueCNT <> 0
      AND DateValueCNT <> 0)
     OR (DateValueCNT <> 0
         AND textvalueCNT <> 0)
     OR (numericValueCNT <> 0
         AND textvalueCNT <> 0)
order by RowSourceDSC, AttributeNM;"

```

Text field can hold almost any type of data. In some cases, the text could be all numeric or it may contain dates. The table below shows fields where the data could be cast as more than one type. (Note: Blank fields can be cast as datatime and often appear in this table.)

```{r DataTYpe, echo= FALSE}
datatype <- selectData(connectionString,query)
datatype <- datatype %>%
  mutate( NumericValuePCT = 100*NumericValueCNT/RowCNT, DateValuePCT = 100*DateValueCNT/RowCNT, TextValuePCT = 100*TextValueCNT/RowCNT) %>%
  select(AttributeNM,RowSourceDSC,NumericValuePCT,  DateValuePCT, TextValuePCT)
  
kable(datatype, digits = 2)
```


```{r daterange, include=FALSE}
query <- "
  SELECT TOP 20
      [rowsourceDSC]
      ,[attributeNM]
      ,[valueTXT]
      ,[CNT]
      ,[AllSourceCNT]
  FROM [SAM].[SourcePatientProfiling].[SummaryPatientSuspiciousValues]
  where attributeNM not in ('PatientStateCD', 'GenderCD', 'PatientCityNM', 'MaritalStatusDSC', 'LanguageDSC', 'EthnicGroupDSC', 'ContactsInLas3YearsNBR','RaceDSC')
  order by CNT DESC
"

```


## Suspicious Values

```{r susp, include=FALSE}
query <- "
  SELECT TOP 20
      [rowsourceDSC]
      ,[attributeNM]
      ,[valueTXT]
      ,[CNT]
      ,[AllSourceCNT]
  FROM [SAM].[SourcePatientProfiling].[SummaryPatientSuspiciousValues]
  where attributeNM not in ('PatientStateCD', 'GenderCD', 'PatientCityNM', 'MaritalStatusDSC', 'LanguageDSC', 'EthnicGroupDSC', 'ContactsInLas3YearsNBR','RaceDSC')
  order by CNT DESC
"

```

Suspicious values occur frequently in the data.  They are often default values or some method of recording nulls that do not represent real information. Some attributes may be shared by a large number of people.  PatientStateCD, GenderCD, PatientCityNM, MaritalStatusDSC, LanguageDSC, EthnicGroupDSC, ContactsInLast3YearsNBR and RaceDSC are not included in the table below. The table below has the top 20 most frequent values in Shared.Person.SourcePatient.

```{r SUspTable, echo= FALSE}
Susp20 <- selectData(connectionString,query)
kable(Susp20, digits = 3)
```




### Address
The most suspicious address fields in Shared.Person.SourcePatient are in the table below. Some of these may be defaults, but another possiblitity is that the address is for a facility such as a prison, a mental health facitily, etc.
```{r address,  echo= FALSE }
query <- "
 SELECT TOP 20
      [rowsourceDSC]
      ,[attributeNM]
      ,[valueTXT]
      ,[CNT]
      ,[AllSourceCNT]
  FROM [SAM].[SourcePatientProfiling].[SummaryPatientSuspiciousValues]
  where attributeNM in ('PatientAddressLine1TXT', 'PatientAddressLine2TXT')
  order by CNT DESC
"
Address <- selectData(connectionString,query)
kable(Address, digits = 3)

```



### Birth and Death Dates
The most frequent dates are often the default dates. The table below has the top 10 most frequent dates.
```{r dates,  echo= FALSE }
query <- "
 SELECT TOP 10
      [rowsourceDSC]
      ,[attributeNM]
      ,[valueTXT]
      ,[CNT]
      ,[AllSourceCNT]
  FROM [SAM].[SourcePatientProfiling].[SummaryPatientSuspiciousValues]
  where attributeNM in ('BirthDTS', 'DeathDTS')
  order by CNT DESC
"
date <- selectData(connectionString,query)
kable(date, digits = 3)

```

### City
The most frequent cities are usually part of the hosiptal geographic area, but there may be innappropriate values that come through too. The table below has the top 10 most frequent cities.
```{r city,  echo= FALSE }
query <- "
 SELECT TOP 10
      [rowsourceDSC]
      ,[attributeNM]
      ,[valueTXT]
      ,[CNT]
      ,[AllSourceCNT]
  FROM [SAM].[SourcePatientProfiling].[SummaryPatientSuspiciousValues]
  where attributeNM in ('PatientCityNM')
  order by CNT DESC
"
city <- selectData(connectionString,query)
kable(city, digits = 3)

```



### Gender
Gender can be coded many different ways, but should be normalized in Shared.Person.SourcePatient.   
```{r gender,  echo= FALSE }
query <- "
 SELECT TOP 10
      [rowsourceDSC]
      ,[attributeNM]
      ,[valueTXT]
      ,[CNT]
      ,[AllSourceCNT]
  FROM [SAM].[SourcePatientProfiling].[SummaryPatientSuspiciousValues]
  where attributeNM in ('GenderCD')
  order by CNT DESC
"
gender <- selectData(connectionString,query)
kable(gender, digits = 3)

```



### First Name
First name may contain default values or variants of names for when a name is unknown.   
```{r firstname,  echo= FALSE }
query <- "
 SELECT TOP 10
      [rowsourceDSC]
      ,[attributeNM]
      ,[valueTXT]
      ,[CNT]
      ,[AllSourceCNT]
  FROM [SAM].[SourcePatientProfiling].[SummaryPatientSuspiciousValues]
  where attributeNM in ('PatientFirstNM')
  order by CNT DESC
"
firstname <- selectData(connectionString,query)
kable(firstname, digits = 3)

```


###Last Name
Last name may contain default values or variants of names for when a name is unknown.   
```{r lastname,  echo= FALSE }
query <- "
 SELECT TOP 10
      [rowsourceDSC]
      ,[attributeNM]
      ,[valueTXT]
      ,[CNT]
      ,[AllSourceCNT]
  FROM [SAM].[SourcePatientProfiling].[SummaryPatientSuspiciousValues]
  where attributeNM in ('PatientLastNM')
  order by CNT DESC
"
lastname <- selectData(connectionString,query)
kable(lastname, digits = 2 )

```


###Medical Record Number (MRN)
Last name may contain default values or variants of names for when a name is unknown.   
```{r MRN,  echo= FALSE }
query <- "
 SELECT TOP 10
      [rowsourceDSC]
      ,[attributeNM]
      ,[valueTXT]
      ,[CNT]
      ,[AllSourceCNT]
  FROM [SAM].[SourcePatientProfiling].[SummaryPatientSuspiciousValues]
  where attributeNM in ('MRN')
  order by CNT DESC
"
MRN <- selectData(connectionString,query)
kable(MRN, digits = )

```

###Primary Care Physician (PCP)
Last name may contain default values or variants of names for when a name is unknown.   
```{r PCP,  echo= FALSE }
query <- "
 SELECT TOP 10
      [rowsourceDSC]
      ,[attributeNM]
      ,[valueTXT]
      ,[CNT]
      ,[AllSourceCNT]
  FROM [SAM].[SourcePatientProfiling].[SummaryPatientSuspiciousValues]
  where attributeNM in ('CurrentPCPID')
  order by CNT DESC
"
PCP <- selectData(connectionString,query)
kable(PCP, digits = 3)
```

###Phone Number
Hight frequency phone number data may be a default value or it may belong to a facility, group home, etc.   
```{r PrimaryPhoneNBR,  echo= FALSE }
query <- "
 SELECT TOP 10
      [rowsourceDSC]
      ,[attributeNM]
      ,[valueTXT]
      ,[CNT]
      ,[AllSourceCNT]
  FROM [SAM].[SourcePatientProfiling].[SummaryPatientSuspiciousValues]
  where attributeNM in ('PrimaryPhoneNBR')
  order by CNT DESC
"
PrimaryPhoneNBR <- selectData(connectionString,query)
kable(PrimaryPhoneNBR, digits = 3)
```

###SSN
Hight frequency SSN data may be a default value, but could indicate another problem (Might be obscured to protect PHI) 
```{r SSN,  echo= FALSE }
query <- "
 SELECT TOP 10
      [rowsourceDSC]
      ,[attributeNM]
      ,[valueTXT]
      ,[CNT]
      ,[AllSourceCNT]
  FROM [SAM].[SourcePatientProfiling].[SummaryPatientSuspiciousValues]
  where attributeNM in ('SSN')
  order by CNT DESC
"
SSN <- selectData(connectionString,query)



if (DisplayPHI) { kable(SSN, digits = 3)

query <- "SELECT   d.rowsourceDSC,
         d.attributeNM,
         valueTXT,
         COUNT(*) AS CNT,
        sum( COUNT(*)) OVER (PARTITION BY ValueTXT, attributeNM) AS AllSourceCNT
FROM     SAM.[SourcePatientProfiling].[PatientAttributesPivotBASE] AS d
where d.AttributeNM = 'SSN'
GROUP BY d.RowSourceDSC, d.attributeNM, ValueTXT
having count(*)>1
order by CNT DESC"

 SSNhist <- selectData(connectionString,query)

head(SSNhist)

hist(SSNhist[SSNhist$CNT<100,]$CNT, 100, xlab = "PatientCount",main = '')
}
```

###State
Hight frequency state data may be a default value, but could indicate another problem   
```{r PatientStateCD,  echo= FALSE }
query <- "
 SELECT TOP 10
      [rowsourceDSC]
      ,[attributeNM]
      ,[valueTXT]
      ,[CNT]
      ,[AllSourceCNT]
  FROM [SAM].[SourcePatientProfiling].[SummaryPatientSuspiciousValues]
  where attributeNM in ('PatientStateCD')
  order by CNT DESC
"
PatientStateCD <- selectData(connectionString,query)
kable(PatientStateCD, digits = 3)
```

###PatientZipCD
Hight frequency zip code data may be a default value, but could indicate another problem   
```{r PatientZipCD,  echo= FALSE }
query <- "
 SELECT TOP 10
      [rowsourceDSC]
      ,[attributeNM]
      ,[valueTXT]
      ,[CNT]
      ,[AllSourceCNT]
  FROM [SAM].[SourcePatientProfiling].[SummaryPatientSuspiciousValues]
  where attributeNM in ('PatientZipCD')
  order by CNT DESC
"
PatientZipCD <- selectData(connectionString,query)
kable(PatientZipCD)
```






###RaceDSC
Hight frequency zip code data may be a default value, but could indicate another problem   
```{r RaceDSC,  echo= FALSE }
query <- "
 SELECT TOP 10
      [rowsourceDSC]
      ,[attributeNM]
      ,[valueTXT]
      ,[CNT]
      ,[AllSourceCNT]
  FROM [SAM].[SourcePatientProfiling].[SummaryPatientSuspiciousValues]
  where attributeNM in ('RaceDSC')
  order by CNT DESC
"
RaceDSC <- selectData(connectionString,query)
kable(RaceDSC)
```

###ReligionDSC
Hight frequency zip code data may be a default value, but could indicate another problem   
```{r ReligionDSC,  echo= FALSE }
query <- "
 SELECT TOP 10
      [rowsourceDSC]
      ,[attributeNM]
      ,[valueTXT]
      ,[CNT]
      ,[AllSourceCNT]
  FROM [SAM].[SourcePatientProfiling].[SummaryPatientSuspiciousValues]
  where attributeNM in ('ReligionDSC')
  order by CNT DESC
"
ReligionDSC <- selectData(connectionString,query)
kable(ReligionDSC)
```

###SubscriberID
Hight frequency subscriberID data may be a default value, but could indicate another problem   
```{r SubscriberID,  echo= FALSE }
query <- "
 SELECT TOP 10
      [rowsourceDSC]
      ,[attributeNM]
      ,[valueTXT]
      ,[CNT]
      ,[AllSourceCNT]
  FROM [SAM].[SourcePatientProfiling].[SummaryPatientSuspiciousValues]
  where attributeNM in ('SubscriberID')
  order by CNT DESC
"
SubscriberID <- selectData(connectionString,query)
kable(SubscriberID)
```
