---
title: "Shared Person Patient Profiling"
output: html_document
---


```{r setup, include=FALSE}
library(healthcareai)
library(dplyr)
library(knitr)
library(tidyr)
knitr::opts_chunk$set(echo = TRUE)
DisplayPHI <- TRUE


# Set connection string for client
connectionString <- "
  driver={SQL Server};
  server=AGCA-edwdev;
  database=SAM;
  trustedConnection=true"


query <- "SELECT DatabaseNM + '.' + SchemaNM + '.' + ViewNM
FROM EDWAdmin.CatalystAdmin.TableBASE
WHERE tableID IN
(
    SELECT [SourceEntityID]
    FROM [EDWAdmin].[CatalystAdmin].[BindingDependencyBASE]
    WHERE bindingID in
    (
        SELECT [BindingID]
        FROM EDWAdmin.CatalystAdmin.BindingBASE
        WHERE DestinationEntityID in
        (
            SELECT tableID
            FROM EDWAdmin.CatalystAdmin.TableBASE
            WHERE schemaNM = 'Person'
                  AND ViewNM = 'SourcePatient'
        )
    )
);"

DependencyList <- selectData(connectionString,query)

```

##Table Dependencies
The dependencies for SourcePatient are **`r as.character(DependencyList[,1])`**.

## Column Utilization
Matching between systems requires the same date on both systems. This table has the fill percentage each field. 

```{r utilization, echo=FALSE}
query <- "with att as (
select ColumnNM as AttributeNM
from EDWAdmin.CatalystAdmin.TableBASE T
inner join EDWAdmin.CatalystAdmin.ColumnBASE C
on t.tableID = c.tableID
where viewNM = 'SourcePatient'
and SchemaNM = 'Person'
 and ColumnNM not in ('BindingID','BindingNM', 'LastLoadDTS', 'PatientID','RowSourceDSC')),
src as (
select distinct rowsourcedsc
from shared.Person.SourcePatient)
, 
attsrc as(
select * from att,src)

SELECT
      atts.[AttributeNM]
      ,atts.[RowSourceDSC]
	 --, case when rowCNT is NULL THEN 0 else 1 end as UsedFLG
,coalesce(100-100*(NullCNT + BlankCNT)/cast(RowCNT as float),0) AS FillPCT

  FROM attsrc atts left outer join 
  [SAM].[SourcePatientProfiling].[SummaryPatientDescriptiveStatisticsBySource]  d
  on atts.attributenm = d.attributeNM and atts.RowSourceDSC = d.RowSourceDSC"
utilization <- selectData(connectionString,query)
utilization <- spread(utilization,RowSourceDSC, FillPCT)

 row.names(utilization)<-utilization$AttributeNM
 utilization <- data.matrix(utilization[,-1])
 
 #heatmap(utilization, Rowv=NA, Colv=NA, col= heat.colors(2), scale="column", margins=c(5,10))
 
kable(utilization, digits = 1)

```

## Fill Rates
```{r fillrates, echo= FALSE}
query <- "
SELECT  top 20
      [AttributeNM]
      ,[RowSourceDSC]
      ,[RowCNT]
      ,[ValueCNT]
      ,[DistinctValueCNT]
      ,[NullCNT]
      ,BlankCNT
      ,100-100*(NullCNT + BlankCNT)/cast(RowCNT as float) AS FillPCT
  FROM [SAM].[SourcePatientProfiling].[SummaryPatientDescriptiveStatisticsBySource]
 
  order by 100-100*(NullCNT + BlankCNT)/cast(RowCNT as float)

 "
FillRate <- selectData(connectionString,query)

 query <- "select count(*)
from shared.Person.SourcePatient"
count <-  selectData(connectionString,query)
 count <- count[1,1]

query <-"SELECT   
      [RowSourceDSC]
      ,100-100*(sum([NullCNT]) +sum(BlankCNT))/cast(sum([RowCNT]) as float) as FillPCT
  FROM [SAM].[SourcePatientProfiling].[SummaryPatientDescriptiveStatisticsBySource]
group by rowsourceDSC"
FillRateBySource <- selectData(connectionString,query)


```
Of the fields that do contain data, the lowest 20 fill rates in Shared.Person.SourcePatient are in the table below. Additional information can be found in the EDW at SAM.SourcePatientProfiling.SummaryPatientDescriptiveStatisticsBySource

```{r tableFillRate, echo= FALSE}
FillRate <- FillRate %>% 
select(AttributeNM, RowSourceDSC, RowCNT, ValueCNT, DistinctValueCNT, NullCNT,BlankCNT, FillPCT)
kable(FillRate, digits =1)
```

## Supicious Data Type 

```{r datatype, include=FALSE}
query <-"SELECT  [AttributeNM],
                [RowSourceDSC],
                [RowCNT],
                DataTypeDSC,
                [NumericValueCNT],
                [DateValueCNT],
                [TextValueCNT]



FROM [SAM].[SourcePatientProfiling].[SummaryPatientDescriptiveStatisticsBySource] summ

WHERE(numericValueCNT <> 0
      AND DateValueCNT <> 0)
     OR (DateValueCNT <> 0
         AND textvalueCNT <> 0)
     OR (numericValueCNT <> 0
         AND textvalueCNT <> 0)
order by RowSourceDSC, AttributeNM;"

```

Text field can hold almost any type of data. In some cases, the text could be all numeric or it may contain dates. The table below shows fields where the data could be cast as more than one type. (Note: Blank fields can be cast as datatime and often appear in this table.)

```{r DataTYpe, echo= FALSE}
datatype <- selectData(connectionString,query)
datatype <- datatype %>%
#  mutate( NumericValuePCT = 100*NumericValueCNT, DateValuePCT = 100*DateValueCNT/RowCNT, TextValuePCT = 100*TextValueCNT/RowCNT) %>%
  select(AttributeNM,RowSourceDSC,DataTypeDSC,NumericValueCNT,  DateValueCNT, TextValueCNT)
  
kable(datatype, digits = 2)
```

## Field Range
```{r daterange, include=FALSE}
query <- "/****** Script for SelectTopNRows command from SSMS  ******/
         select     
	    d.AttributeNM
                  ,d.RowSourceDSC
			   , t.DataTypeDSC
			   ,MIN(d.ValueTXT ) AS RawMinVAL
	       , MAX(d.ValueTXT) AS RawMaxVAL   
			   ,min(TRY_CONVERT (NUMERIC, d.ValueTXT)) as NumericMinVal
			   ,avg(TRY_CONVERT (NUMERIC, d.ValueTXT)) as NumericAvgVal
			   ,max(TRY_CONVERT (NUMERIC, d.ValueTXT)) as NumericMaxVal
FROM     SAM.[SourcePatientProfiling].[PatientAttributesPivotBASE]  as d
inner join SAM.[SourcePatientProfiling].[SharedPersonProfilingEventPatientAttributeDataTypes] as t
on d.attributeNM= t.attributeNM --and t.DataTypeDSC like 'num%'
where valueTXT <> '' and valueTXT is not NULL
GROUP BY d.AttributeNM, d.RowSourceDSC, t.datatypedsc
order by  RowSourceDSC, AttributeNM
"

fvalue <-  selectData(connectionString,query)

```
The characturistics of the data in the fields can sometiems point to a suspicious item.  For example, fields that are abnormally long or have a value that is outside the range expected.  This table should some descriptive statistics of the values in each data field 

``` {r tablechare , , echo= FALSE}
kable(fvalue, digits = 1)
```


##Field Character Length
```{r fcharelength, echo= FALSE}
query <- "/****** Script for SelectTopNRows command from SSMS  ******/
SELECT 
           [AttributeNM]
      ,[RowSourceDSC]
    ,[MinLengthVAL]
      ,[MeanVAL]
      ,[MaxLengthVAL]
  FROM [SAM].[SourcePatientProfiling].[SummaryPatientDescriptiveStatisticsBySource]"

flength <-  selectData(connectionString,query)
kable(flength, digits = 3)
```

## Most Frequent Values

```{r susp, include=FALSE}
query <- "
  SELECT TOP 20
      [rowsourceDSC]
      ,[attributeNM]
      ,[valueTXT]
      ,[CNT]
      ,[AllSourceCNT]
  FROM [SAM].[SourcePatientProfiling].[SummaryPatientSuspiciousValues]
  where attributeNM not in ('PatientStateCD', 'GenderCD', 'PatientCityNM', 'MaritalStatusDSC', 'LanguageDSC', 'EthnicGroupDSC', 'ContactsInLas3YearsNBR','RaceDSC')
  order by CNT DESC
"

```

When a value occurs often in a data set, that may mean it is default values or some method of recording nulls.  These values might not represent real information. However there are attributes may be shared by a large number of people.  PatientStateCD, GenderCD, PatientCityNM, MaritalStatusDSC, LanguageDSC, EthnicGroupDSC, ContactsInLast3YearsNBR and RaceDSC are not included in the table below. The table below has the top 20 most frequent values in Shared.Person.SourcePatient.

```{r SUspTable, echo= FALSE}
Susp20 <- selectData(connectionString,query)
kable(Susp20, digits = 3)
```




### Address
The most suspicious address fields in Shared.Person.SourcePatient are in the table below. Some of these may be defaults, but another possiblitity is that the address is for a facility such as a prison, a mental health facitily, etc.
```{r address,  echo= FALSE }
query <- "
 SELECT TOP 20
      [rowsourceDSC]
      ,[attributeNM]
      ,[valueTXT]
      ,[CNT]
      ,[AllSourceCNT]
  FROM [SAM].[SourcePatientProfiling].[SummaryPatientSuspiciousValues]
  where attributeNM in ('PatientAddressLine1TXT', 'PatientAddressLine2TXT')
  order by CNT DESC
"
Address <- selectData(connectionString,query)
kable(Address, digits = 3)

```



### Birth and Death Dates
The most frequent dates are often the default dates. The table below has the top 20 most frequent dates.
```{r dates,  echo= FALSE }
query <- "
 SELECT TOP 20
      [rowsourceDSC]
      ,[attributeNM]
      ,[valueTXT]
      ,[CNT]
      ,[AllSourceCNT]
  FROM [SAM].[SourcePatientProfiling].[SummaryPatientSuspiciousValues]
  where attributeNM in ('BirthDTS', 'DeathDTS')
  order by CNT DESC
"
date <- selectData(connectionString,query)
kable(date, digits = 3)

```

### City
The most frequent cities are usually part of the hosiptal geographic area, but there may be innappropriate values that come through too. The table below has the top 20 most frequent cities.
```{r city,  echo= FALSE }
query <- "
 SELECT TOP 20
      [rowsourceDSC]
      ,[attributeNM]
      ,[valueTXT]
      ,[CNT]
      ,[AllSourceCNT]
  FROM [SAM].[SourcePatientProfiling].[SummaryPatientSuspiciousValues]
  where attributeNM in ('PatientCityNM')
  order by CNT DESC
"
city <- selectData(connectionString,query)
kable(city, digits = 3)

```



### Gender
Gender can be coded many different ways, but should be normalized in Shared.Person.SourcePatient.   
```{r gender,  echo= FALSE }
query <- "
 SELECT TOP 20
      [rowsourceDSC]
      ,[attributeNM]
      ,[valueTXT]
      ,[CNT]
      ,[AllSourceCNT]
  FROM [SAM].[SourcePatientProfiling].[SummaryPatientSuspiciousValues]
  where attributeNM in ('GenderCD')
  order by CNT DESC
"
gender <- selectData(connectionString,query)
kable(gender, digits = 3)

```



### First Name
First name may contain default values or variants of names for when a name is unknown.   
```{r firstname,  echo= FALSE }
query <- "
 SELECT TOP 20
      [rowsourceDSC]
      ,[attributeNM]
      ,[valueTXT]
      ,[CNT]
      ,[AllSourceCNT]
  FROM [SAM].[SourcePatientProfiling].[SummaryPatientSuspiciousValues]
  where attributeNM in ('PatientFirstNM')
  order by CNT DESC
"
firstname <- selectData(connectionString,query)
kable(firstname, digits = 3)

```


###Last Name
Last name may contain default values or variants of names for when a name is unknown.   
```{r lastname,  echo= FALSE }
query <- "
 SELECT TOP 20
      [rowsourceDSC]
      ,[attributeNM]
      ,[valueTXT]
      ,[CNT]
      ,[AllSourceCNT]
  FROM [SAM].[SourcePatientProfiling].[SummaryPatientSuspiciousValues]
  where attributeNM in ('PatientLastNM')
  order by CNT DESC
"
lastname <- selectData(connectionString,query)
kable(lastname, digits = 2 )

```


###Medical Record Number (MRN)
Last name may contain default values or variants of names for when a name is unknown.   
```{r MRN,  echo= FALSE }
query <- "
 SELECT TOP 20
      [rowsourceDSC]
      ,[attributeNM]
      ,[valueTXT]
      ,[CNT]
      ,[AllSourceCNT]
  FROM [SAM].[SourcePatientProfiling].[SummaryPatientSuspiciousValues]
  where attributeNM in ('MRN')
  order by CNT DESC
"
MRN <- selectData(connectionString,query)
kable(MRN, digits = )

```

###Primary Care Physician (PCP)
Last name may contain default values or variants of names for when a name is unknown.   
```{r PCP,  echo= FALSE }
query <- "
 SELECT TOP 20
      [rowsourceDSC]
      ,[attributeNM]
      ,[valueTXT]
      ,[CNT]
      ,[AllSourceCNT]
  FROM [SAM].[SourcePatientProfiling].[SummaryPatientSuspiciousValues]
  where attributeNM in ('CurrentPCPID')
  order by CNT DESC
"
PCP <- selectData(connectionString,query)
kable(PCP, digits = 3)
```

###Phone Number
Hight frequency phone number data may be a default value or it may belong to a facility, group home, etc.   
```{r PrimaryPhoneNBR,  echo= FALSE }
query <- "
 SELECT TOP 20
      [rowsourceDSC]
      ,[attributeNM]
      ,[valueTXT]
      ,[CNT]
      ,[AllSourceCNT]
  FROM [SAM].[SourcePatientProfiling].[SummaryPatientSuspiciousValues]
  where attributeNM in ('PrimaryPhoneNBR')
  order by CNT DESC
"
PrimaryPhoneNBR <- selectData(connectionString,query)
kable(PrimaryPhoneNBR, digits = 3)
```

###SSN
Hight frequency SSN data may be a default value, but could indicate another problem (Might be obscured to protect PHI) 
```{r SSN,  echo= FALSE }
query <- "
 SELECT TOP 20
      [rowsourceDSC]
      ,[attributeNM]
      ,[valueTXT]
      ,[CNT]
      ,[AllSourceCNT]
  FROM [SAM].[SourcePatientProfiling].[SummaryPatientSuspiciousValues]
  where attributeNM in ('SSN')
  order by CNT DESC
"
SSN <- selectData(connectionString,query)



if (DisplayPHI) { kable(SSN, digits = 3)

query <- "SELECT   d.rowsourceDSC,
         d.attributeNM,
         valueTXT,
         COUNT(*) AS CNT,
        sum( COUNT(*)) OVER (PARTITION BY ValueTXT, attributeNM) AS AllSourceCNT
FROM     SAM.[SourcePatientProfiling].[PatientAttributesPivotBASE] AS d
where d.AttributeNM = 'SSN' and valuetxt <> ''
GROUP BY d.RowSourceDSC, d.attributeNM, ValueTXT
having count(*)>1
order by CNT DESC" }

 SSNhist <- selectData(connectionString,query)

kable(head(SSNhist))

hist(SSNhist[SSNhist$CNT<100,]$CNT, 100, xlab = "PatientCount",main = '')


```

###State
Hight frequency state data may be a default value, but could indicate another problem   
```{r PatientStateCD,  echo= FALSE }
query <- "
 SELECT TOP 20
      [rowsourceDSC]
      ,[attributeNM]
      ,[valueTXT]
      ,[CNT]
      ,[AllSourceCNT]
  FROM [SAM].[SourcePatientProfiling].[SummaryPatientSuspiciousValues]
  where attributeNM in ('PatientStateCD')
  order by CNT DESC
"
PatientStateCD <- selectData(connectionString,query)
kable(PatientStateCD, digits = 3)
```

###PatientZipCD
Hight frequency zip code data may be a default value, but could indicate another problem   
```{r PatientZipCD,  echo= FALSE }
query <- "
 SELECT TOP 20
      [rowsourceDSC]
      ,[attributeNM]
      ,[valueTXT]
      ,[CNT]
      ,[AllSourceCNT]
  FROM [SAM].[SourcePatientProfiling].[SummaryPatientSuspiciousValues]
  where attributeNM in ('PatientZipCD')
  order by CNT DESC
"
PatientZipCD <- selectData(connectionString,query)
kable(PatientZipCD)
```






###RaceDSC
Hight frequency zip code data may be a default value, but could indicate another problem   
```{r RaceDSC,  echo= FALSE }
query <- "
 SELECT TOP 20
      [rowsourceDSC]
      ,[attributeNM]
      ,[valueTXT]
      ,[CNT]
      ,[AllSourceCNT]
  FROM [SAM].[SourcePatientProfiling].[SummaryPatientSuspiciousValues]
  where attributeNM in ('RaceDSC')
  order by CNT DESC
"
RaceDSC <- selectData(connectionString,query)
kable(RaceDSC)
```

###ReligionDSC
Hight frequency zip code data may be a default value, but could indicate another problem   
```{r ReligionDSC,  echo= FALSE }
query <- "
 SELECT TOP 20
      [rowsourceDSC]
      ,[attributeNM]
      ,[valueTXT]
      ,[CNT]
      ,[AllSourceCNT]
  FROM [SAM].[SourcePatientProfiling].[SummaryPatientSuspiciousValues]
  where attributeNM in ('ReligionDSC')
  order by CNT DESC
"
ReligionDSC <- selectData(connectionString,query)
kable(ReligionDSC)
```

###SubscriberID
Hight frequency subscriberID data may be a default value, but could indicate another problem   
```{r SubscriberID,  echo= FALSE }
query <- "
 SELECT TOP 20
      [rowsourceDSC]
      ,[attributeNM]
      ,[valueTXT]
      ,[CNT]
      ,[AllSourceCNT]
  FROM [SAM].[SourcePatientProfiling].[SummaryPatientSuspiciousValues]
  where attributeNM in ('SubscriberID')
  order by CNT DESC
"
SubscriberID <- selectData(connectionString,query)
kable(SubscriberID)
```
