---
title: "Post Merge Report"
output: html_document
---


```{r setup, include=FALSE}
library(healthcareai)
library(dplyr)
knitr::opts_chunk$set(echo = TRUE)

connectionString <- '
  driver={SQL Server};
  server=qu-edwdev;
  database=SAM;
  trustedConnection=true'
query <- '
SELECT [PatientSource]
      ,[UniquePatientCNT]
  FROM [SAM].[MasterDataMonitoring].[PatientIDReconV5]'
Recon <- selectData(connectionString,query)
```
## Incoming records
The multivue process is expected to output few EDWPatientIDs than it recieves and all EDWPatientIDs should arrive in MasterPatient.Patient. 
```{r tablercon, echo= FALSE}
Recon
```
##Suspicious Records
EDWPatientIDs may group together different numbers of patient identities.  If a patient is only represesnted once then they will have their own EDWPatientID.  If too many are merged together it may be a sign that something unusual has happened.
```{r HighFrequency, echo= FALSE}
query <- 'SELECT 
      [EDWPatientIdCNT]
      ,[FrequncyCNT]
  FROM [SAM].[MasterDataMonitoring].[EdwPatientIDHighFrequncyV5]'
freq <- selectData(connectionString,query) 
plot(freq, type = 'h', lwd = 10, main = 'Merge Count', lend = 'square' , log= 'y')
```

THe most suspicious of these are:

```{r suspiciousmerge, echo= FALSE}

query <- 'SELECT top 5
      [EDWPatientID]
      ,[EDWPatientIdCNT]
  FROM [SAM].[MasterDataMonitoring].[EDWPatientIDFrequencyV5]
  order by EDWPatientIDCNT desc'

suspect <- selectData(connectionString,query) 
head(suspect, 20)
```

## Load History
The number of records loaded can be helpful for troubleshooting.

```{r loadhistory, echo= FALSE}
query <- 'SELECT  
--[EntityType]
      --,
[DateCreated]
      ,[SourcePatientCNT]
      ,[VirtualPatientCNT]
      ,[MergedPatientCNT]
  FROM [SAM].[MasterDataMonitoring].[MultiVueCountHistoryV5]'

history <- selectData(connectionString,query) 
history
```
