```{r titleconfig, echo=FALSE}
domain <- "Patient"
rule <- "Patient"
```
---
title: `r paste( domain, "Post Match Report")`
output:
  html_document: default

---

```{r setup, include=FALSE}
library(healthcareai)
library(dplyr)
library(knitr)
library(tidyr)
knitr::opts_chunk$set(echo = TRUE)
options(knitr.kable.NA = '')




connectionString <- '
  driver={SQL Server};
  server=agca-edwdev;
  database=SAM;
  trustedConnection=true'

```


##Verification
```{r verification, echo=FALSE}
query <- paste( "select count(*)
  from MultiVueDataSync.",domain,".",rule, sep = "")

totalrecords <-  selectData(connectionString,query)
totalrecords <- totalrecords[1,1]

query <- paste("select
       Count(*) AS PatientCNT
FROM   shared.person.source" , domain,sep = "")

totalSourcerecords <-  selectData(connectionString,query)

query <- paste("select rowsourcedsc as Source, count(*) as RecordCNT
    from [MultiVueDataSync].",domain,".[EntitySources] E
    LEFT OUTER JOIN [MultiVueDataSync].",domain,".",rule, " AS Patient1
    ON E.VirtualId = patient1.identifier
    group by rowsourcedsc"
, sep = "")

sourcerecords <- selectData(connectionString,query)



```

The number of total number of records processed is  `r  totalrecords` out of `r totalSourcerecords` in Share Person. The number of records from each source is in the table below.

```{r sourcerecords, echo=FALSE}
kable(sourcerecords)

```

##Match Combination Count


```{r matchcombo, echo=FALSE}
query <- paste(
 "select count(*)
  from MultiVueDataSync.",domain,".","Match", sep = "")

totalmatches <-  selectData(connectionString,query)
totalmatches <- totalmatches[1,1]


```

Matching records are a pair of records that scored high enough to be above the match threshold. These matching pairs of records are candidates to be merged. There are `r totalmatches` pairs of matching records. The matches can occur between different sources.  The breakdown of these matches between the sources is in the table below.

```{r matchmatrix, echo= FALSE}
query <- paste("SELECT e1.source as Source, e2.source as Source2,count(*)as  MatchCNT
FROM   [MultiVueDataSync].",domain,".[Match] AS M
       INNER JOIN
       [MultiVueDataSync].",domain,".[EntitySources] AS E1
       ON m.VirtualEntity1Id = e1.VirtualId
       INNER JOIN
       [MultiVueDataSync].",domain,".[EntitySources] AS E2
       ON m.VirtualEntity2Id = e2.VirtualId
       LEFT OUTER JOIN
       [MultiVueDataSync].",domain,".",rule," AS Patient1
       ON M.VirtualEntity1Id = patient1.identifier
       LEFT OUTER JOIN
       [MultiVueDataSync].",domain,".",rule," AS Patient2
       ON M.VirtualEntity2Id = patient2.identifier
        group by e1.source, e2.source", sep = "")

matchmatrix<- selectData(connectionString,query)
matchmatrix <- spread(matchmatrix,Source2, MatchCNT)
kable(matchmatrix)
```

```{r scoredist , include=FALSE}

query <- paste("
  SELECT 
      [Score]
	 , count(score) as ScoreCNT 
  FROM [MultiVueDataSync].",domain,".[Match] M
  group by score", sep = "")
ScoreFreq <- selectData(connectionString,query)


```



## Score Distribution



After the MultiVue match process is run a data sync was run to retrieve data from MultiVue.  This data is a score for each pair of records that broke the matching threshold. The distribution of score shows which scores contain the most matches.


```{r Distribution, echo=FALSE }
plot(ScoreFreq, type = 'h', lwd = 10, main = 'Score Distribution', lend = 'square'  )

```

 

```{r top scores, echo=FALSE}
tot <- sum(ScoreFreq$ScoreCNT)
top8 <- ScoreFreq %>%
  arrange(desc(ScoreCNT)) %>%
  head(n=8) %>%
  mutate(ScorePCT = 100*ScoreCNT/totalmatches ) %>%
  arrange(desc(ScoreCNT))
```
From this distribution the prominent peaks are if the most interest in finding the merge threshold. Preform a validation test on these peaks to find which neighborhood the merge threshold should be in.The peaks account for `r sprintf("%3.1f",100*sum(top8$ScoreCNT)/tot)`% of the possible matches.


```{r top scores table, echo=FALSE}
kable(top8, digits = 1)

```

Those scoring groups have the following score breakdowns:

```{r scoredetails , echo= FALSE}
query <- paste(" select distinct  sd.[Hash] ,SD.totalscore as Score,   
 -- SDG.GroupName,           SDG.GroupScore,            
   F.FieldIdentifier,             F.MatchType
   --,             F.Score as FieldScore    
  from  MultiVueDataSync.",domain,".[ScoringDetails] SD      LEFT OUTER JOIN MultiVueDataSync.",domain,".[ScoringDetailsGroups] SDG    ON SDG.ScoringDetails_Id = SD.id     
   LEFT OUTER JOIN MultiVueDataSync.",domain,".[ScoringDetailsGroupField] F   ON F.ScoringDetailsGroups_Id = SDG.id  order by sd.totalscore desc",sep="")

scoredetails2 <- selectData(connectionString,query)

query <- paste("   SELECT [Hash], count(*) as Count
  FROM [MultiVueDataSync].",domain,".[ScoringDetails]
  group by Hash
  order by count(*)", sep="")
hashcount <- selectData(connectionString,query)


scoredetails <- scoredetails2 %>%
spread( FieldIdentifier,MatchType) %>%
inner_join(.,hashcount,by = "Hash") %>%
arrange(Score) %>%
select(-Hash)

names(scoredetails)<-gsub(domain,'',names(scoredetails))

kable(scoredetails)

```


##Validation Set


``` {r validation , echo= FALSE}

query <- "SELECT  
      [MatchID]
      ,[VirtualEntity1Id]
      ,[VirtualEntity2Id]
      ,[Domain]
      ,[Score]
      ,[Source1]
      ,[Source2]
      ,[EntityID1]
      ,[EntityID2]
      ,[ID1]
      ,[ID2]
      ,[Identifier1]
      ,[Identifier2]
      ,[PatientFirstNM1]
      ,[PatientFirstNM2]
      ,[PatientLastNM1]
      ,[PatientLastNM2]
      ,[SSN1]
      ,[SSN2]
  FROM [SAM].[MasterDataMonitoring].[PostMatchValidationSample]"
#validationset  <- selectData(connectionString,query)
#kable(validationset)
query <- paste("SELECT TOP 10000 * FROM   [MultiVueDataSync].",domain,".[Match] AS M
       INNER JOIN
       [MultiVueDataSync].",domain,".[EntitySources] AS E1
       ON m.VirtualEntity1Id = e1.VirtualId
       INNER JOIN
       [MultiVueDataSync].",domain,".[EntitySources] AS E2
       ON m.VirtualEntity2Id = e2.VirtualId
       LEFT OUTER JOIN
       [MultiVueDataSync].",domain,".",rule," AS Patient1
       ON M.VirtualEntity1Id = patient1.identifier
       LEFT OUTER JOIN
       [MultiVueDataSync].",domain,".",rule," AS Patient2
       ON M.VirtualEntity2Id = patient2.identifier
       where E1.EntityID like '[A-Z]%' OR E2.EntityId like '[A-Z]%'", sep="")

sample <-  selectData(connectionString,query)
```