---
title: "Post Match Report"
output:
  html_document: default
---

```{r setup, include=FALSE}
library(healthcareai)
library(dplyr)
knitr::opts_chunk$set(echo = TRUE)

connectionString <- '
  driver={SQL Server};
  server=qu-edwdev;
  database=SAM;
  trustedConnection=true'
query <- '/****** Script for SelectTopNRows command from SSMS  ******/
SELECT 
      [Score]
      ,[ScoreCNT]
  FROM [SAM].[MasterDataMonitoring].[PostMatchScoreFrequency]'
ScoreFreq <- selectData(connectionString,query)
```

## Score Distribution



After the MultiVue match process is run a data sync was run to retrieve data from MultiVue.  This data is a score for each pair of records that broke the matching threshold. The distribution of score shows which scores contain the most matches.


```{r Distribution, echo=FALSE }
plot(ScoreFreq, type = 'h', lwd = 1, main = 'Score Distribution', lend = 'square' )
```

 

```{r top scores, echo=FALSE}
tot <- sum(ScoreFreq$ScoreCNT)
top5 <- ScoreFreq %>%
  arrange(desc(ScoreCNT)) %>%
  head(n=5) %>%
  arrange(desc(Score))
```
From this distribution the prominent peaks are if the most interest in finding the merge threshold. Preform a validation test on these peaks to find which neighborhood the merge threshold should be in.The peaks account for `r sprintf("%3.1f",100*sum(top5$ScoreCNT)/tot)`% of the possible matches.


```{r top scores table, echo=FALSE}
top5

```

Those scoring groups have the following score breakdowns:

```{r scoredetails }
query <- 'SELECT  distinct
      m.[Score]
      --,[ScoreDetailsID]
      --,[MatchRuleName]
     -- ,[Hash]
     -- ,[ScoreDetailGroupID]
      ,[GroupName]
      ,[GroupScore]
     -- ,[ThresholdApplied]
      --,[ScoreBeforeLimitApplied]
      --,[ScoreDetailGroupFieldID]
      ,[FieldIdentifier]
      ,[MatchType]
      ,[FieldScore]
    --  ,[ScoreReduction]
  FROM [SAM].[MasterDataMonitoring].[PostMatchScoreDetail] m
  where m.Score in (SELECT top 5
      [Score]
  FROM [SAM].[MasterDataMonitoring].[PostMatchScoreFrequency] 
  order by ScoreCNT desc)'
scoredetails <- selectData(connectionString,query)
scoredetails
```