---
title: "Shared Person Patient Profiling"
output: html_document
---


```{r setup, include=FALSE}
library(healthcareai)
library(dplyr)
library(knitr)
knitr::opts_chunk$set(echo = TRUE)

connectionString <- '
  driver={SQL Server};
  server=qu-edwdev;
  database=SAM;
  trustedConnection=true'
query <- '

SELECT TOP 10
      [AttributeNM]
      ,[RowSourceDSC]
      ,[RowCNT]
      ,[ValueCNT]
      ,[DistinctValueCNT]
      ,[NullCNT]
      ,BlankCNT
      ,100*1-(NullCNT + BlankCNT)/cast(RowCNT as float) AS FillPCT
  
  FROM [SAM].[SourcePatientProfiling].[SummaryPatientDescriptiveStatisticsBySource]
  order by 100-100*(NullCNT + BlankCNT)/cast(RowCNT as float) '
FillRate <- selectData(connectionString,query)

query <-"SELECT   
      [RowSourceDSC]
      ,100-100*(sum([NullCNT]) +sum(BlankCNT))/cast(sum([RowCNT]) as float) as FillPCT
  FROM [SAM].[SourcePatientProfiling].[SummaryPatientDescriptiveStatisticsBySource]
group by rowsourceDSC"
FillRateBySource <- selectData(connectionString,query)

```

## Fill Rates
For a field to be useful it must contain data.  The lowest 10 fill rates in Shared.Person.SourcePatient are in the table below. Additional information can be found in the EDW at SAM.SourcePatientProfiling.SummaryPatientDescriptiveStatisticsBySource

```{r tableFillRate, echo= FALSE}
kable(FillRate, digits =2)
```

## Data Type 

```{r datatype, include=FALSE}
query <-"SELECT  [AttributeNM],
                [RowSourceDSC],
                [RowCNT],
                [NumericValueCNT],
                [DateValueCNT],
                [TextValueCNT]



FROM [SAM].[SourcePatientProfiling].[SummaryPatientDescriptiveStatisticsBySource] summ

WHERE(numericValueCNT <> 0
      AND DateValueCNT <> 0)
     OR (DateValueCNT <> 0
         AND textvalueCNT <> 0)
     OR (numericValueCNT <> 0
         AND textvalueCNT <> 0)
order by RowSourceDSC, AttributeNM;"

```

Text field can hold almost any type of data. In some cases, the text could be all numeric or it may contain dates. THe table below shows fields where the data could be cast as more than one type

```{r DataTYpe, echo= FALSE}
datatype <- selectData(connectionString,query)
datatype <- datatype %>%
  mutate( NumericValuePCT = 100*NumericValueCNT/RowCNT, DateValuePCT = 100*DateValueCNT/RowCNT, TextValuePCT = 100*TextValueCNT/RowCNT) %>%
  select(AttributeNM,RowSourceDSC,NumericValuePCT,  DateValuePCT, TextValuePCT)
  
kable(datatype, digits = 2)
```
## Data Range
```{r daterange, include=FALSE}
query <- "
  SELECT TOP 20
      [rowsourceDSC]
      ,[attributeNM]
      ,[valueTXT]
      ,[CNT]
      ,[AllSourceCNT]
  FROM [SAM].[SourcePatientProfiling].[SummaryPatientSuspiciousValues]
  where attributeNM not in ('PatientStateCD', 'GenderCD', 'PatientCityNM', 'MaritalStatusDSC', 'LanguageDSC', 'EthnicGroupDSC', 'ContactsInLas3YearsNBR','RaceDSC')
  order by CNT DESC
"

```


## Suspicious Values

```{r susp, include=FALSE}
query <- "
  SELECT TOP 20
      [rowsourceDSC]
      ,[attributeNM]
      ,[valueTXT]
      ,[CNT]
      ,[AllSourceCNT]
  FROM [SAM].[SourcePatientProfiling].[SummaryPatientSuspiciousValues]
  where attributeNM not in ('PatientStateCD', 'GenderCD', 'PatientCityNM', 'MaritalStatusDSC', 'LanguageDSC', 'EthnicGroupDSC', 'ContactsInLas3YearsNBR','RaceDSC')
  order by CNT DESC
"

```

Suspicious values occur frequently in the data.  They are often default values or some method of recording nulls that do not represent real information. Some attributes may be shared by a large number of people.  PatientStateCD, GenderCD, PatientCityNM, MaritalStatusDSC, LanguageDSC, EthnicGroupDSC, ContactsInLast3YearsNBR and RaceDSC are not included in the table below. The table below has the top 20 most frequent values in Shared.Person.SourcePatient.

```{r SUspTable, echo= FALSE}
Susp20 <- selectData(connectionString,query)
kable(Susp20, digits = 3)
```




### Address
The most suspicious address fields in Shared.Person.SourcePatient are in the table below. Some of these may be defaults, but another possiblitity is that the address is for a facility such as a prison, a mental health facitily, etc.
```{r address,  echo= FALSE }
query <- "
 SELECT TOP 20
      [rowsourceDSC]
      ,[attributeNM]
      ,[valueTXT]
      ,[CNT]
      ,[AllSourceCNT]
  FROM [SAM].[SourcePatientProfiling].[SummaryPatientSuspiciousValues]
  where attributeNM in ('PatientAddressLine1TXT', 'PatientAddressLine2TXT')
  order by CNT DESC
"
Address <- selectData(connectionString,query)
kable(Address, digits = 3)

```



### Birth and Death Dates
The most frequent dates are often the default dates. The table below has the top 10 most frequent dates.
```{r dates,  echo= FALSE }
query <- "
 SELECT TOP 10
      [rowsourceDSC]
      ,[attributeNM]
      ,[valueTXT]
      ,[CNT]
      ,[AllSourceCNT]
  FROM [SAM].[SourcePatientProfiling].[SummaryPatientSuspiciousValues]
  where attributeNM in ('BirthDTS', 'DeathDTS')
  order by CNT DESC
"
date <- selectData(connectionString,query)
kable(date, digits = 3)

```

### City
The most frequent cities are usually part of the hosiptal geographic area, but there may be innappropriate values that come through too. The table below has the top 10 most frequent cities.
```{r city,  echo= FALSE }
query <- "
 SELECT TOP 10
      [rowsourceDSC]
      ,[attributeNM]
      ,[valueTXT]
      ,[CNT]
      ,[AllSourceCNT]
  FROM [SAM].[SourcePatientProfiling].[SummaryPatientSuspiciousValues]
  where attributeNM in ('PatientCityNM')
  order by CNT DESC
"
city <- selectData(connectionString,query)
kable(city, digits = 3)

```



### Gender
Gender can be coded many different ways, but should be normalized in Shared.Person.SourcePatient.   
```{r gender,  echo= FALSE }
query <- "
 SELECT TOP 10
      [rowsourceDSC]
      ,[attributeNM]
      ,[valueTXT]
      ,[CNT]
      ,[AllSourceCNT]
  FROM [SAM].[SourcePatientProfiling].[SummaryPatientSuspiciousValues]
  where attributeNM in ('GenderCD')
  order by CNT DESC
"
gender <- selectData(connectionString,query)
kable(gender, digits = 3)

```



### First Name
First name may contain default values or varients of names for when a name is unknown.   
```{r firstname,  echo= FALSE }
query <- "
 SELECT TOP 10
      [rowsourceDSC]
      ,[attributeNM]
      ,[valueTXT]
      ,[CNT]
      ,[AllSourceCNT]
  FROM [SAM].[SourcePatientProfiling].[SummaryPatientSuspiciousValues]
  where attributeNM in ('PatientFirstNM')
  order by CNT DESC
"
firstname <- selectData(connectionString,query)
kable(firstname, digits = 3)

```


###Last Name
Last name may contain default values or varients of names for when a name is unknown.   
```{r lastname,  echo= FALSE }
query <- "
 SELECT TOP 10
      [rowsourceDSC]
      ,[attributeNM]
      ,[valueTXT]
      ,[CNT]
      ,[AllSourceCNT]
  FROM [SAM].[SourcePatientProfiling].[SummaryPatientSuspiciousValues]
  where attributeNM in ('PatientLastNM')
  order by CNT DESC
"
lastname <- selectData(connectionString,query)
kable(lastname, digits = 2 )

```


###Medical Record Number (MRN)
Last name may contain default values or varients of names for when a name is unknown.   
```{r MRN,  echo= FALSE }
query <- "
 SELECT TOP 10
      [rowsourceDSC]
      ,[attributeNM]
      ,[valueTXT]
      ,[CNT]
      ,[AllSourceCNT]
  FROM [SAM].[SourcePatientProfiling].[SummaryPatientSuspiciousValues]
  where attributeNM in ('MRN')
  order by CNT DESC
"
MRN <- selectData(connectionString,query)
kable(MRN, digits = )

```

###Primary Care Physician (PCP)
Last name may contain default values or varients of names for when a name is unknown.   
```{r PCP,  echo= FALSE }
query <- "
 SELECT TOP 10
      [rowsourceDSC]
      ,[attributeNM]
      ,[valueTXT]
      ,[CNT]
      ,[AllSourceCNT]
  FROM [SAM].[SourcePatientProfiling].[SummaryPatientSuspiciousValues]
  where attributeNM in ('CurrentPCPID')
  order by CNT DESC
"
PCP <- selectData(connectionString,query)
kable(PCP, digits = 3)
```

###Phone Number
Hight frequency phone number data may be a default value or it may belong to a facility, group home, etc.   
```{r PrimaryPhoneNBR,  echo= FALSE }
query <- "
 SELECT TOP 10
      [rowsourceDSC]
      ,[attributeNM]
      ,[valueTXT]
      ,[CNT]
      ,[AllSourceCNT]
  FROM [SAM].[SourcePatientProfiling].[SummaryPatientSuspiciousValues]
  where attributeNM in ('PrimaryPhoneNBR')
  order by CNT DESC
"
PrimaryPhoneNBR <- selectData(connectionString,query)
kable(PrimaryPhoneNBR, digits = 3)
```

###SSN
Hight frequency SSN data may be a default value, but could indicate another problem   
```{r SSN,  echo= FALSE }
query <- "
 SELECT TOP 10
      [rowsourceDSC]
      ,[attributeNM]
      ,[valueTXT]
      ,[CNT]
      ,[AllSourceCNT]
  FROM [SAM].[SourcePatientProfiling].[SummaryPatientSuspiciousValues]
  where attributeNM in ('SSN')
  order by CNT DESC
"
SSN <- selectData(connectionString,query)
kable(SSN, digits = 3)
```

###State
Hight frequency state data may be a default value, but could indicate another problem   
```{r PatientStateCD,  echo= FALSE }
query <- "
 SELECT TOP 10
      [rowsourceDSC]
      ,[attributeNM]
      ,[valueTXT]
      ,[CNT]
      ,[AllSourceCNT]
  FROM [SAM].[SourcePatientProfiling].[SummaryPatientSuspiciousValues]
  where attributeNM in ('PatientStateCD')
  order by CNT DESC
"
PatientStateCD <- selectData(connectionString,query)
kable(PatientStateCD, digits = 3)
```

###PatientZipCD
Hight frequency zip code data may be a default value, but could indicate another problem   
```{r PatientZipCD,  echo= FALSE }
query <- "
 SELECT TOP 10
      [rowsourceDSC]
      ,[attributeNM]
      ,[valueTXT]
      ,[CNT]
      ,[AllSourceCNT]
  FROM [SAM].[SourcePatientProfiling].[SummaryPatientSuspiciousValues]
  where attributeNM in ('PatientZipCD')
  order by CNT DESC
"
PatientZipCD <- selectData(connectionString,query)
kable(PatientZipCD)
```






###RaceDSC
Hight frequency zip code data may be a default value, but could indicate another problem   
```{r RaceDSC,  echo= FALSE }
query <- "
 SELECT TOP 10
      [rowsourceDSC]
      ,[attributeNM]
      ,[valueTXT]
      ,[CNT]
      ,[AllSourceCNT]
  FROM [SAM].[SourcePatientProfiling].[SummaryPatientSuspiciousValues]
  where attributeNM in ('RaceDSC')
  order by CNT DESC
"
RaceDSC <- selectData(connectionString,query)
kable(RaceDSC)
```

###ReligionDSC
Hight frequency zip code data may be a default value, but could indicate another problem   
```{r ReligionDSC,  echo= FALSE }
query <- "
 SELECT TOP 10
      [rowsourceDSC]
      ,[attributeNM]
      ,[valueTXT]
      ,[CNT]
      ,[AllSourceCNT]
  FROM [SAM].[SourcePatientProfiling].[SummaryPatientSuspiciousValues]
  where attributeNM in ('ReligionDSC')
  order by CNT DESC
"
ReligionDSC <- selectData(connectionString,query)
kable(ReligionDSC)
```

###SubscriberID
Hight frequency zip code data may be a default value, but could indicate another problem   
```{r SubscriberID,  echo= FALSE }
query <- "
 SELECT TOP 10
      [rowsourceDSC]
      ,[attributeNM]
      ,[valueTXT]
      ,[CNT]
      ,[AllSourceCNT]
  FROM [SAM].[SourcePatientProfiling].[SummaryPatientSuspiciousValues]
  where attributeNM in ('SubscriberID')
  order by CNT DESC
"
SubscriberID <- selectData(connectionString,query)
kable(SubscriberID)
```
