---
title: "Shared Person Provider Profiling"
output: html_document
---


```{r setup, include=FALSE}
library(healthcareai)
library(dplyr)
library(knitr)
knitr::opts_chunk$set(echo = TRUE)
DisplayPHI <- TRUE


connectionString <- "
  driver={SQL Server};
  server=AGCA-edwdev;
  database=SAM;
  trustedConnection=true"
```

```{r, dependencies, echo = FALSE}
query <- "SELECT DatabaseNM + '.' + SchemaNM + '.' + ViewNM
FROM EDWAdmin.CatalystAdmin.TableBASE
WHERE tableID IN
(
    SELECT [SourceEntityID]
    FROM [EDWAdmin].[CatalystAdmin].[BindingDependencyBASE]
    WHERE bindingID =
    (
        SELECT [BindingID]
        FROM EDWAdmin.CatalystAdmin.BindingBASE
        WHERE DestinationEntityID =
        (
            SELECT tableID
            FROM EDWAdmin.CatalystAdmin.TableBASE
            WHERE schemaNM = 'Person'
                  AND ViewNM = 'SourceProvider'
        )
    )
);"

DependencyList <- selectData(connectionString,query)

```

##Table Dependencies
The dependencies for SourceProvider are **`r as.character(DependencyList[,1])`**






```{r, fillrate , echo= FALSE}
query <- "
SELECT TOP 10
      [AttributeNM]
      ,[RowSourceDSC]
      ,[RowCNT]
      ,[ValueCNT]
      ,[DistinctValueCNT]
      ,[NullCNT]
      ,BlankCNT
  FROM [SAM].[SourceProviderProfiling].[SummaryProviderDescriptiveStatisticsBySource]
  order by 100-100*(NullCNT + BlankCNT)/cast(RowCNT as float) "
FillRate <- selectData(connectionString,query)

 query <- "select count(*)
from shared.Person.SourceProvider"
count <-  selectData(connectionString,query)
 count <- count[1,1]

query <-"SELECT   
      [RowSourceDSC]
      ,100-100*(sum([NullCNT]) +sum(BlankCNT))/cast(sum([RowCNT]) as float) as FillPCT
  FROM [SAM].[SourceProviderProfiling].[SummaryProviderDescriptiveStatisticsBySource]
group by rowsourceDSC"
FillRateBySource <- selectData(connectionString,query)

query <- " select  columnNM as AttributeNM
  from EDWAdmin.CatalystAdmin.TableBASe T
  inner join   EDWAdmin.CatalystAdmin.ColumnBASE C
  on T.tableID = C.tableID
  where databaseNM = 'shared'
  and schemanm = 'Person'
  and tableNM = 'SourceProviderBASE'
  and ColumnNM not in ('BindingID','BindingNM', 'LastLoadDTS','ProviderID','RowSourceDSC')

  Except

  SELECT distinct
      [AttributeNM]

  
  FROM [SAM].[SourceProviderProfiling].[SummaryProviderDescriptiveStatisticsBySource]"

UnUsedList <- FillRateBySource <- selectData(connectionString,query,)

```

## Fill Rates
For a field to be useful it must contain data. The fields **`r as.character(UnUsedList[,1])`** contain only NULLS and are not represented in this analysis.  The lowest 10 fill rates in Shared.Person.SourceProvider are in the table below. Additional information can be found in the EDW at SAM.SourceProviderProfiling.SummaryProviderDescriptiveStatisticsBySource

```{r tableFillRate, echo= FALSE}
FillRate <- FillRate %>% 
 mutate(RowCNT = count, NullCNT = count - ValueCNT) %>%
 mutate( FillPCT = 100-100*(NullCNT + BlankCNT)/RowCNT) %>%
select(AttributeNM, RowSourceDSC, RowCNT, ValueCNT, DistinctValueCNT, NullCNT,BlankCNT, FillPCT)
kable(FillRate, digits =1)
```


## Supicious Data Type 

```{r datatype, include=FALSE}
query <-"SELECT  [AttributeNM],
                [RowSourceDSC],
                [RowCNT],
                [NumericValueCNT],
                [DateValueCNT],
                [TextValueCNT]



FROM [SAM].[SourceProviderProfiling].[SummaryProviderDescriptiveStatisticsBySource] summ

WHERE(numericValueCNT <> 0
      AND DateValueCNT <> 0)
     OR (DateValueCNT <> 0
         AND textvalueCNT <> 0)
     OR (numericValueCNT <> 0
         AND textvalueCNT <> 0)
order by RowSourceDSC, AttributeNM;"

```

Text field can hold almost any type of data. In some cases, the text could be all numeric or it may contain dates. The table below shows fields where the data could be cast as more than one type. (Note: Blank fields can be cast as datatime and often appear in this table.)

```{r DataTYpe, echo= FALSE}
datatype <- selectData(connectionString,query)
datatype <- datatype %>%
  mutate( NumericValuePCT = 100*NumericValueCNT/RowCNT, DateValuePCT = 100*DateValueCNT/RowCNT, TextValuePCT = 100*TextValueCNT/RowCNT) %>%
  select(AttributeNM,RowSourceDSC,NumericValuePCT,  DateValuePCT, TextValuePCT)
  
kable(datatype, digits = 2)
```


```{r daterange, include=FALSE}
query <- "
  SELECT TOP 20
      [rowsourceDSC]
      ,[attributeNM]
      ,[valueTXT]
      ,[CNT]
      ,[AllSourceCNT]
  FROM [SAM].[SourceProviderProfiling].[SummaryProviderSuspiciousValues]
  where attributeNM not in ('PatientStateCD', 'GenderCD', 'PatientCityNM', 'MaritalStatusDSC', 'LanguageDSC', 'EthnicGroupDSC', 'ContactsInLas3YearsNBR','RaceDSC')
  order by CNT DESC
"

```


## Suspicious Values

```{r susp, include=FALSE}
query <- "
  SELECT TOP 20
      [rowsourceDSC]
      ,[attributeNM]
      ,[valueTXT]
      ,[CNT]
      ,[AllSourceCNT]
  FROM [SAM].[SourceProviderProfiling].[SummaryProviderSuspiciousValues]

  order by CNT DESC
"

```

Suspicious values occur frequently in the data.  They are often default values or some method of recording nulls that do not represent real information. . The table below has the top 20 most frequent values in Shared.Person.SourceProvider.

```{r SUspTable, echo= FALSE}
Susp20 <- selectData(connectionString,query)
kable(Susp20, digits = 3)
```






### Primary Specialty
The table below has the top 10 most frequent specialities.
```{r dates,  echo= FALSE }
query <- "
 SELECT TOP 10
      [rowsourceDSC]
      ,[attributeNM]
      ,[valueTXT]
      ,[CNT]
      ,[AllSourceCNT]
  FROM [SAM].[SourceProviderProfiling].[SummaryProviderSuspiciousValues]
  where attributeNM in ('PrimarySpecialtyCD', 'PrimarySpecialtyNM')
  order by CNT DESC
"
date <- selectData(connectionString,query)
kable(date, digits = 3)

```









### First Name
First name may contain default values or variants of names for when a name is unknown. The table below are the top 10 most frequent provider first names.   
```{r firstname,  echo= FALSE }
query <- "
 SELECT TOP 10
      [rowsourceDSC]
      ,[attributeNM]
      ,[valueTXT]
      ,[CNT]
      ,[AllSourceCNT]
  FROM [SAM].[SourceProviderProfiling].[SummaryProviderSuspiciousValues]
  where attributeNM in ('ProviderFirstNM')
  order by CNT DESC
"
firstname <- selectData(connectionString,query)
kable(firstname, digits = 3)

```


### Middle name
Middle name may contain default values or variants of names for when a name is unknown. The table below are the top 10 most frequent provider middle names.   
```{r middlename,  echo= FALSE }
query <- "
 SELECT TOP 10
      [rowsourceDSC]
      ,[attributeNM]
      ,[valueTXT]
      ,[CNT]
      ,[AllSourceCNT]
  FROM [SAM].[SourceProviderProfiling].[SummaryProviderSuspiciousValues]
  where attributeNM in ('ProviderMiddleNM')
  order by CNT DESC
"
middlename <- selectData(connectionString,query)
kable(middlename, digits = 2 )

```


###Last Name
Last name may contain default values or variants of names for when a name is unknown. The table below are the top 10 most frequent provider last names.   
```{r lastname,  echo= FALSE }
query <- "
 SELECT TOP 10
      [rowsourceDSC]
      ,[attributeNM]
      ,[valueTXT]
      ,[CNT]
      ,[AllSourceCNT]
  FROM [SAM].[SourceProviderProfiling].[SummaryProviderSuspiciousValues]
  where attributeNM in ('ProviderLastNM')
  order by CNT DESC
"
lastname <- selectData(connectionString,query)
kable(lastname, digits = 2 )

```

###Name Suffix
Name may contain default values or variants of names for when a name is unknown.   
```{r PCP,  echo= FALSE }
query <- "
 SELECT TOP 10
      [rowsourceDSC]
      ,[attributeNM]
      ,[valueTXT]
      ,[CNT]
      ,[AllSourceCNT]
  FROM [SAM].[SourceProviderProfiling].[SummaryProviderSuspiciousValues]
  where attributeNM in ('ProviderSuffixNM')
  order by CNT DESC
"
PCP <- selectData(connectionString,query)
kable(PCP, digits = 3)
```

###NPI
NPI may contain default values.   
```{r MRN,  echo= FALSE }
if (DisplayPHI) {query <- "
 SELECT TOP 10
      [rowsourceDSC]
      ,[attributeNM]
      ,[valueTXT]
      ,[CNT]
      ,[AllSourceCNT]
  FROM [SAM].[SourceProviderProfiling].[SummaryProviderSuspiciousValues]
  where attributeNM in ('NPI')
  order by CNT DESC
"
MRN <- selectData(connectionString,query)
kable(MRN, digits = )
}

```








