---
title: "Patient Post Match Report"
output:
  html_document: default
---

```{r setup, include=FALSE}
library(healthcareai)
library(dplyr)
library(knitr)
library(tidyr)
knitr::opts_chunk$set(echo = TRUE)
options(knitr.kable.NA = '')

domain <- "Patient"
rule <- "Patient"

connectionString <- '
  driver={SQL Server};
  server=agca-edwdev;
  database=SAM;
  trustedConnection=true'

```
##Verification
```{r verification, echo=FALSE}
query <- paste(
 "select count(*)
  from MultiVueDataSync.",domain,".",rule, sep = "")

totalmatches <-  selectData(connectionString,query)
totalmatches <- totalmatches[1,1]

```

The number of total matches is  `r  totalmatches`

##Match Combinations

```{r matchcombo, echo=FALSE}
 query <- paste("SELECT e1.source as Source1, e2.source as Source2,count(*)as  MatchCNT
FROM   [MultiVueDataSync].",domain,".[Match] AS M
       INNER JOIN
       [MultiVueDataSync].",domain,".[EntitySources] AS E1
       ON m.VirtualEntity1Id = e1.VirtualId
       INNER JOIN
       [MultiVueDataSync].",domain,".[EntitySources] AS E2
       ON m.VirtualEntity2Id = e2.VirtualId
       LEFT OUTER JOIN
       [MultiVueDataSync].",domain,".",rule," AS Patient1
       ON M.VirtualEntity1Id = patient1.identifier
       LEFT OUTER JOIN
       [MultiVueDataSync].",domain,".",rule," AS Patient2
       ON M.VirtualEntity2Id = patient2.identifier
        group by e1.source, e2.source", sep = "")

matchmatrix<- selectData(connectionString,query)
matchmatrix <- spread(matchmatrix,Source2, MatchCNT)
kable(matchmatrix)





```





```{r scoredist , include=FALSE}

query <- paste("
  SELECT 
      [Score]
	 , count(score) as ScoreCNT 
  FROM [MultiVueDataSync].",domain,".[Match] M
  group by score", sep = "")
ScoreFreq <- selectData(connectionString,query)


"SELECT min([TotalScore]), max(totalscore)
  
  FROM [MultiVueDataSync].[Patient].[ScoringDetails]"
```



## Score Distribution



After the MultiVue match process is run a data sync was run to retrieve data from MultiVue.  This data is a score for each pair of records that broke the matching threshold. The distribution of score shows which scores contain the most matches.


```{r Distribution, echo=FALSE }
plot(ScoreFreq, type = 'h', lwd = 10, main = 'Score Distribution', lend = 'square'  )

```

 

```{r top scores, echo=FALSE}
tot <- sum(ScoreFreq$ScoreCNT)
top8 <- ScoreFreq %>%
  arrange(desc(ScoreCNT)) %>%
  head(n=8) %>%
  mutate(ScorePCT = 100*ScoreCNT/totalmatches ) %>%
  arrange(desc(ScoreCNT))
```
From this distribution the prominent peaks are if the most interest in finding the merge threshold. Preform a validation test on these peaks to find which neighborhood the merge threshold should be in.The peaks account for `r sprintf("%3.1f",100*sum(top8$ScoreCNT)/tot)`% of the possible matches.


```{r top scores table, echo=FALSE}
kable(top8)

```

Those scoring groups have the following score breakdowns:

```{r scoredetails , echo= FALSE}
query <- paste("select distinct
		  SD.totalscore,
		  F.Score,
		  SDG.GroupName,
            SDG.GroupScore,
            F.FieldIdentifier,
            F.MatchType,
            F.Score as FieldScore
    from
	MultiVueDataSync.",domain,".[ScoringDetails] SD
     LEFT OUTER JOIN MultiVueDataSync.",domain,".[ScoringDetailsGroups] SDG
	  ON SDG.ScoringDetails_Id = SD.id
     LEFT OUTER JOIN MultiVueDataSync.",domain,".[ScoringDetailsGroupField] F 
	ON F.ScoringDetailsGroups_Id = SDG.id;", sep = "")
scoredetails <- selectData(connectionString,query)
kable(scoredetails)
```





``` {r validation , echo= FALSE}

query <- "SELECT  
      [MatchID]
      ,[VirtualEntity1Id]
      ,[VirtualEntity2Id]
      ,[Domain]
      ,[Score]
      ,[Source1]
      ,[Source2]
      ,[EntityID1]
      ,[EntityID2]
      ,[ID1]
      ,[ID2]
      ,[Identifier1]
      ,[Identifier2]
      ,[PatientFirstNM1]
      ,[PatientFirstNM2]
      ,[PatientLastNM1]
      ,[PatientLastNM2]
      ,[SSN1]
      ,[SSN2]
  FROM [SAM].[MasterDataMonitoring].[PostMatchValidationSample]"
#validationset  <- selectData(connectionString,query)
#kable(validationset)


```